Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-28 ms.tex

\begin{figure}
  \includegraphics[width=\columnwidth]{TI.pdf}
  \caption{
 }
\label{fig:TI}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{TI.pdf}
  \caption{Minimum effective wind heating parameter required for thermal stability as a function of SMBH mass.  Black lines show $v_{\rm TI}$ (eq.~[\ref{eq:cooling3}]), the heating rate required for $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}} > 10$ in the high-heating limit when the stagnation radius lies interior to the influence radius, for different values of the mass loss parameter $\eta$ as marked.    {\bf Blue ???}  lines show the minimum heating parameter required to have $\zeta > \zeta_c = (r_{b}/r_{\rm inf})^{0.5(1-\Gamma)}$ (eq.~[\ref{eq:zetacrit}]), separately for cusp (solid) and core (dashed) galaxies, using the mean $r_{b}/r_{\rm inf} \approx 7.6M_{\bullet,8}^{-0.2}$ from the \citet{LauerFaber+:2007a} galaxy sample.  For $\zeta < \zeta_c$ the stagnation radius moves from inside the influence radius, out to the stellar break radius $r_b$ (Appendix \ref{app:be}); in practice renders the flow susceptible to thermal runaway, even if $v_{w} > v_{\rm TI}$.  For cusp galaxies the $v_w > v_{\rm TI}$ is usually the more strigent criterion for stability, while for core galaxies the $\zeta > \zeta_c$ is usually more relevant.  
 }
\label{fig:TI}
\end{figure}
